---
title: "Study 1_OpenScript_MindsetXInfidelity"
author: "Tris"
date: "2023-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}

library(readr)
library(psych)
library(car)
library(tidyverse)
library(Hmisc)
library(ppcor)
library(lessR)
library(corrplot)
library(tidyr)
library(lm.beta)

```
## Load Data and set wd
```{r}
setwd("...")

MindInfi_1 <- read.csv("....Study1_DataR.csv")
```

# Descriptives 

```{r}
names(MindInfi_1)
table(MindInfi_1$gender)
table(MindInfi_1$nation_group, MindInfi_1$gender)
table((MindInfi_1$Age))
```

# Reverse coding items, chronbachs alpha, creating scales

```{r}

names(MindInfi_1)

#SOI

##Bx
alpha(MindInfi_1[,c("SOI_1", "SOI_2", "SOI_3")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(SOI_Bx = select(. ,c(SOI_1, SOI_2, SOI_3)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$SOI_Bx)


##attitudes
MindInfi_1$SOI_6R <- recode(MindInfi_1$SOI_6, '1=5; 2=4; 3=3; 4=2; 5=1')

str(MindInfi_1$SOI_6R)
str(MindInfi_1$SOI_6)

alpha(MindInfi_1[,c("SOI_4", "SOI_5", "SOI_6R")])

###Scale
MindInfi_1 <- MindInfi_1 %>%
  mutate(SOI_Att = select(. ,c(SOI_4, SOI_5, SOI_6R)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$SOI_Att)


##desires
alpha(MindInfi_1[,c ("SOI_7", "SOI_8", "SOI_9")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(SOI_Des = select(. ,c(SOI_7, SOI_8, SOI_9)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$SOI_Att)


##SOI-total
alpha(MindInfi_1[,c("SOI_1", "SOI_2", "SOI_3", "SOI_4", "SOI_5", "SOI_6R", "SOI_7", "SOI_8", "SOI_9")])



#Attachment
##Anxiety

MindInfi_1$ECR_8R <- car::recode(MindInfi_1$ECR_8, '1=5; 2=4; 3=3; 4=2; 5=1')

psych::alpha(MindInfi_1[,c("ECR_2", "ECR_4", "ECR_6", "ECR_8R", "ECR_10", "ECR_12")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(AnxiousAttachment =  dplyr::select(. ,c(ECR_2, ECR_4, ECR_6, ECR_8R, ECR_10, ECR_12)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$AnxiousAttachment)



##Avoidance

MindInfi_1$ECR_1R <- car::recode(MindInfi_1$ECR_1, '1=5; 2=4; 3=3; 4=2; 5=1')
MindInfi_1$ECR_5R <- car::recode(MindInfi_1$ECR_5, '1=5; 2=4; 3=3; 4=2; 5=1')
MindInfi_1$ECR_9R <- car::recode(MindInfi_1$ECR_9, '1=5; 2=4; 3=3; 4=2; 5=1')

str(MindInfi_1$ECR_9R)
str(MindInfi_1$ECR_9)

psych::alpha(MindInfi_1[,c("ECR_1R", "ECR_3", "ECR_5R", "ECR_7", "ECR_9R", "ECR_11")])


###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(AvoidanceAttachment = dplyr::select(. ,c(ECR_1R, ECR_3, ECR_5R, ECR_7, ECR_9R, ECR_11)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$AvoidancecAttachment)


#Personality
## Extraversion

MindInfi_1$TIPI_6R <- recode(MindInfi_1$TIPI_6, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
str(MindInfi_1$TIPI_6R)
str(MindInfi_1$TIPI_6)

alpha(MindInfi_1[,c("TIPI_1", "TIPI_6R")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(Extraversion = select(. ,c(TIPI_1, TIPI_6R)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$Extraversion)

##Agreeableness
MindInfi_1$TIPI_2R <- recode(MindInfi_1$TIPI_2, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
alpha(MindInfi_1[,c("TIPI_2R", "TIPI_7")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(Agreeableness = select(. ,c(TIPI_2R, TIPI_7)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$Agreeableness)

##Conscientiousness
MindInfi_1$TIPI_8R <- recode(MindInfi_1$TIPI_8, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
alpha(MindInfi_1[,c("TIPI_3", "TIPI_8R")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(Conscientiousness = select(. ,c(TIPI_3, TIPI_8R)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$Conscientiousness)

##Emotional Stability
MindInfi_1$TIPI_4R <- recode(MindInfi_1$TIPI_4, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
alpha(MindInfi_1[,c("TIPI_4R", "TIPI_9")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(EmotionalStability = select(. ,c(TIPI_4R, TIPI_9)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$EmotionalStability)

##OpennesstoExperiences
MindInfi_1$TIPI_10R <- recode(MindInfi_1$TIPI_10, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
alpha(MindInfi_1[,c("TIPI_5", "TIPI_10R")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(OpenessExperiences = select(. ,c(TIPI_5, TIPI_10R)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$OpenessExperiences)

#AttitudesInfidelity

MindInfi_1$AttitInfid_2R <- car::recode(MindInfi_1$AttitInfid_2, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
MindInfi_1$AttitInfid_5R <- car::recode(MindInfi_1$AttitInfid_5, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
MindInfi_1$AttitInfid_6R <- car::recode(MindInfi_1$AttitInfid_6, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
MindInfi_1$AttitInfid_7R <- car::recode(MindInfi_1$AttitInfid_7, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
MindInfi_1$AttitInfid_8R <- car::recode(MindInfi_1$AttitInfid_8, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')
MindInfi_1$AttitInfid_12R <- car::recode(MindInfi_1$AttitInfid_12, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')

alpha(MindInfi_1[,c("AttitInfid_1", "AttitInfid_2R", "AttitInfid_3", "AttitInfid_4", "AttitInfid_5R", "AttitInfid_6R", "AttitInfid_7R", "AttitInfid_8R", "AttitInfid_9", "AttitInfid_10", "AttitInfid_11", "AttitInfid_12R")])


###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(AttitudesInfidelity = dplyr::select(. ,c(AttitInfid_1, AttitInfid_2R, AttitInfid_3, AttitInfid_4, AttitInfid_5R, AttitInfid_6R, AttitInfid_7R, AttitInfid_8R, AttitInfid_9, AttitInfid_10, AttitInfid_11, AttitInfid_12R)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$AttitudesInfidelity)

#IntentsInfidelity
MindInfi_1$IntentInfid_3R <- car::recode(MindInfi_1$IntentInfid_3, '1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1')

alpha(MindInfi_1[,c("IntentInfid_1", "IntentInfid_2", "IntentInfid_3R", "IntentInfid_4", "IntentInfid_5", "IntentInfid_6", "IntentInfid_7")])

###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(IntentionsInfidelity = dplyr::select(. ,c(IntentInfid_1, IntentInfid_2, IntentInfid_3R, IntentInfid_4, IntentInfid_5, IntentInfid_6, IntentInfid_7)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$IntentionsInfidelity)


#Mindset

mean(MindInfi_1$TightLoose_1)
mean(MindInfi_1$TightLoose_2)
mean(MindInfi_1$TightLoose_3)
mean(MindInfi_1$TightLoose_4, na.rm = TRUE)
mean(MindInfi_1$TightLoose_5R, na.rm = TRUE)
mean(MindInfi_1$TightLoose_6)

sd(MindInfi_1$TightLoose_1)
sd(MindInfi_1$TightLoose_2)
sd(MindInfi_1$TightLoose_3)
sd(MindInfi_1$TightLoose_4, na.rm = TRUE)
sd(MindInfi_1$TightLoose_5R, na.rm = TRUE)
sd(MindInfi_1$TightLoose_6)

MindInfi_1$TightLoose_5R <- car::recode(MindInfi_1$TightLoose_5, '1=6; 2=5; 3=4; 4=3; 5=2; 6=1')

str(MindInfi_1$TightLoose_5R)
str(MindInfi_1$TightLoose_5)

psych::alpha(MindInfi_1[,c("TightLoose_1", "TightLoose_2", "TightLoose_3", "TightLoose_4", "TightLoose_5R", "TightLoose_6")])

names(MindInfi_1)
#item total correlations:
MindInfi_1$Total_Score1 <- rowSums(MindInfi_1[, c("TightLoose_1", "TightLoose_2", 
    "TightLoose_3", "TightLoose_4", "TightLoose_5R", "TightLoose_6")])

item_names1 <- c("TightLoose_1", "TightLoose_2", "TightLoose_3", "TightLoose_4", "TightLoose_5R", "TightLoose_6")

item_total_correlations1 <- sapply(item_names1, function(item) {
  correlation <- cor(MindInfi_1[[item]], MindInfi_1$Total_Score1, use = "pairwise.complete.obs")
  p_value <- cor.test(MindInfi_1[[item]], MindInfi_1$Total_Score1, use = "pairwise.complete.obs")$p.value
  c(correlation = correlation, p_value = p_value)
})

# Print item-total correlations and their p-values
item_total_correlations1


###Scale

MindInfi_1 <- MindInfi_1 %>%
  mutate(MindsetScale = dplyr::select(. ,c(TightLoose_1, TightLoose_2, TightLoose_3, TightLoose_4, TightLoose_5R, TightLoose_6)) %>% rowMeans(na.rm = TRUE))

head(MindInfi_1$MindsetScale)
summary(MindInfi_1$MindsetScale)
```

# Creating new data frame for just attachment to filter out NA values

```{r}
ECROnly1.0 <- MindInfi_1[ ,c("AnxiousAttachment", "AvoidanceAttachment", "MindsetScale", "IntentionsInfidelity", "AttitudesInfidelity")]

ECROnly = ECROnly[!is.na(ECROnly$AnxiousAttachment),]

head(ECROnly$AnxiousAttachment)
head(ECROnly$AvoidanceAttachment)

summary(ECROnly$AnxiousAttachment)
```

# Running correlations

```{r}

cor.test(MindInfi_1$IntentionsInfidelity, 
         MindInfi_1$AttitudesInfidelity, 
         method = "pearson")

cor.test(MindInfi_1$MindsetScale, 
         MindInfi_1$AttitudesInfidelity, 
         method = "pearson")

cor.test(MindInfi_1$MindsetScale, 
         MindInfi_1$IntentionsInfidelity, 
         method = "pearson")

names(MindInfi_1)

rcorr(as.matrix(MindInfi_1[, c("IntentionsInfidelity", 
                               "AttitudesInfidelity", 
                               "MindsetScale")], 
                type = "pearson"))

rcorr(as.matrix(MindInfi_1[, c("IntentionsInfidelity", 
                               "AttitudesInfidelity",
                               "MindsetScale",
                               "OpenessExperiences", 
                               "Conscientiousness",
                               "Extraversion", 
                               "Agreeableness", 
                               "EmotionalStability")], 
                type = "pearson"))

rcorr(as.matrix(MindInfi_1[, c("IntentionsInfidelity", 
                               "AttitudesInfidelity",
                               "MindsetScale",
                               "SOI_Bx",
                               "SOI_Att",
                               "SOI_Des")], 
                type = "pearson"))

rcorr(as.matrix(ECROnly[, c("IntentionsInfidelity", 
                               "AttitudesInfidelity",
                               "MindsetScale",
                            "AvoidanceAttachment",
                               "AnxiousAttachment")], 
                type = "pearson"))

##Partial correlations for intentions

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$OpenessExperiences,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Conscientiousness,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Extraversion,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Agreeableness,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$EmotionalStability,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Bx,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Att,
          method = "pearson")

pcor.test(MindInfi_1$IntentionsInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Des,
          method = "pearson")

pcor.test(ECROnly$IntentionsInfidelity,
          ECROnly$MindsetScale,
          ECROnly$AvoidanceAttachment,
          method = "pearson")

pcor.test(ECROnly1.0$IntentionsInfidelity,
          ECROnly1.0$MindsetScale,
          ECROnly1.0$AnxiousAttachment,
          method = "pearson")

##partial correlations for attitudes

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$OpenessExperiences,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Conscientiousness,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Extraversion,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$Agreeableness,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$EmotionalStability,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Bx,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Att,
          method = "pearson")

pcor.test(MindInfi_1$AttitudesInfidelity,
          MindInfi_1$MindsetScale,
          MindInfi_1$SOI_Des,
          method = "pearson")

pcor.test(ECROnly$AttitudesInfidelity,
          ECROnly$MindsetScale,
          ECROnly$AvoidanceAttachment,
          method = "pearson")

pcor.test(ECROnly1.0$AttitudesInfidelity,
          ECROnly1.0$MindsetScale,
          ECROnly1.0$AnxiousAttachment,
          method = "pearson")
```

# Hierarchial Linear Regressions & nested models: SOI: Attitudes & Intentions

```{r}

names(MindInfi_1)

#Step/Block 1: using lm for linear modelling : 
#Rules of thumb for R-squared (small = .01, med = .09, large = .25)

Step1Att <- lm(AttitudesInfidelity ~ gender + nation_group, 
            data = MindInfi_1)

summary(Step1Att)

Step1_Att.beta <- lm.beta(Step1Att)
summary(Step1_Att.beta)

#Step/Block2:

Step2_AttSOI <- lm(AttitudesInfidelity ~ gender + nation_group + 
                  SOI_Bx +
                  SOI_Att + 
                  SOI_Des,
                data = MindInfi_1)

nrow(model.frame(Step2_AttSOI))

summary(Step2_AttSOI)

Step2_AttSOI.beta <- lm.beta(Step2_AttSOI)
summary(Step2_AttSOI.beta)

#Step/Block3:

Step3_AttSOIMind <- lm(AttitudesInfidelity ~ gender + nation_group + 
                  SOI_Bx +
                  SOI_Att + 
                  SOI_Des +
                    MindsetScale,
                data = MindInfi_1)

nrow(model.frame(Step3_AttSOIMind))

summary(Step3_AttSOIMind)

#standardized beta coefficients

Step3_AttSOIMind.beta <- lm.beta(Step3_AttSOIMind)
summary(Step3_AttSOIMind.beta)

#Nested model comparison

anova(Step1Att, Step2_AttSOI, Step3_AttSOIMind)

#Change in R-squared (incremental variance explained)
summary(Step2_AttSOI)$r.squared

summary(Step3_AttSOIMind)$adj.r.squared - summary(Step2_AttSOI)$adj.r.squared

###Intentions

Step1Intent <- lm(IntentionsInfidelity ~ gender + nation_group, 
            data = MindInfi_1)

Step2_IntentSOI <- lm(IntentionsInfidelity ~ gender + nation_group +
                 SOI_Bx +
                  SOI_Att + 
                  SOI_Des,    
            data = MindInfi_1)

Step3_IntentSOIMind <- lm(IntentionsInfidelity ~ gender + nation_group +
                 SOI_Bx +
                  SOI_Att + 
                  SOI_Des +
                   MindsetScale,    
            data = MindInfi_1)

Step1Intent.beta <- lm.beta(Step1Intent)
Step2_IntentSOI.beta <- lm.beta(Step2_IntentSOI)
Step3_IntentSOIMind.beta <- lm.beta(Step3_IntentSOIMind)

summary(Step1Intent.beta)
summary(Step2_IntentSOI.beta)
summary(Step3_IntentSOIMind.beta)

summary(Step2_IntentSOI)$adj.r.squared - summary(Step1Intent)$adj.r.squared
summary(Step3_IntentSOIMind)$adj.r.squared - summary(Step2_IntentSOI)$adj.r.squared

anova(Step1Intent, Step2_IntentSOI, Step3_IntentSOIMind)
```

# Hierarchial Linear Regressions & nested models: Personality: Attitudes & Intentions

```{r}
## Attitudes
names(MindInfi_1)

Step2_AttBig5 <- lm(AttitudesInfidelity ~ gender + nation_group +
                 OpenessExperiences +
                  Conscientiousness + 
                  Extraversion +
                   Agreeableness +
                   EmotionalStability,
            data = MindInfi_1)

Step3_AttBig5Mind <- lm(AttitudesInfidelity ~ gender + nation_group +
                  OpenessExperiences +
                  Conscientiousness + 
                  Extraversion +
                   Agreeableness +
                   EmotionalStability +
                   MindsetScale,    
            data = MindInfi_1)


Step2_AttBig5.beta <- lm.beta(Step2_AttBig5)
Step3_AttBig5Mind.beta <- lm.beta(Step3_AttBig5Mind)

summary(Step1_Att.beta)
summary(Step2_AttBig5.beta)
summary(Step3_AttBig5Mind.beta)

summary(Step2_AttBig5)$adj.r.squared - summary(Step1Att)$adj.r.squared
summary(Step3_AttBig5Mind)$adj.r.squared - summary(Step2_AttBig5)$adj.r.squared

anova(Step1Att, Step2_AttBig5, Step3_AttBig5Mind)


###Intentions

Step2_IntentBig5 <- lm(IntentionsInfidelity ~ gender + nation_group +
                 OpenessExperiences +
                  Conscientiousness + 
                  Extraversion +
                   Agreeableness +
                   EmotionalStability,
            data = MindInfi_1)

Step3_IntentBig5Mind <- lm(IntentionsInfidelity ~ gender + nation_group +
                  OpenessExperiences +
                  Conscientiousness + 
                  Extraversion +
                   Agreeableness +
                   EmotionalStability +
                   MindsetScale,    
            data = MindInfi_1)


Step2_IntentBig5.beta <- lm.beta(Step2_IntentBig5)
Step3_IntentBig5Mind.beta <- lm.beta(Step3_IntentBig5Mind)

summary(Step1Intent.beta)
summary(Step2_IntentBig5.beta)
summary(Step3_IntentBig5Mind.beta)

summary(Step2_IntentBig5)$adj.r.squared - summary(Step1Intent)$adj.r.squared
summary(Step3_IntentBig5Mind)$adj.r.squared - summary(Step2_IntentBig5)$adj.r.squared

anova(Step1Intent, Step2_IntentBig5, Step3_IntentBig5Mind)

```

# Hierarchial Linear Regressions & nested models: Attachment: Attitudes & Intentions


```{r}
names(ECROnly)

#Attitudes

Step1_Att_ECR <- lm(AttitudesInfidelity ~ gender + nation_group,
                    data = ECROnly)


Step2_AttAttachment <- lm(AttitudesInfidelity ~ gender + nation_group +
                AnxiousAttachment +
                  AvoidanceAttachment,
            data = ECROnly)

Step3_AttAttachMind <- lm(AttitudesInfidelity ~ gender + nation_group +
                  AnxiousAttachment +
                  AvoidanceAttachment +
                   MindsetScale,    
            data = ECROnly)

Step1_Att_ECR.beta <- lm.beta(Step1_Att_ECR)
Step2_AttAttachment.beta <- lm.beta(Step2_AttAttachment)
Step3_AttAttachMind.beta <- lm.beta(Step3_AttAttachMind)

summary(Step1_Att_ECR.beta)
summary(Step2_AttAttachment.beta)
summary(Step3_AttAttachMind.beta)

summary(Step2_AttAttachment)$adj.r.squared - summary(Step1_Att_ECR)$adj.r.squared
summary(Step3_AttAttachMind)$adj.r.squared - summary(Step2_AttAttachment)$adj.r.squared

anova(Step1_Att_ECR, Step2_AttAttachment, Step3_AttAttachMind)


###Intentions

Step1_Intent_ECR <- lm(IntentionsInfidelity ~ gender + nation_group,
                    data = ECROnly)


Step2_IntentAttachment <- lm(IntentionsInfidelity ~ gender + nation_group +
                AnxiousAttachment +
                  AvoidanceAttachment,
            data = ECROnly)

Step3_IntentAttachMind <- lm(IntentionsInfidelity ~ gender + nation_group +
                  AnxiousAttachment +
                  AvoidanceAttachment +
                   MindsetScale,    
            data = ECROnly)

Step1_Intent_ECR.beta <- lm.beta(Step1_Intent_ECR)
Step2_IntentAttachment.beta <- lm.beta(Step2_IntentAttachment)
Step3_IntentAttachMind.beta <- lm.beta(Step3_IntentAttachMind)

summary(Step1_Intent_ECR.beta)
summary(Step2_IntentAttachment.beta)
summary(Step3_IntentAttachMind.beta)

summary(Step2_IntentAttachment)$adj.r.squared - summary(Step1_Intent_ECR)$adj.r.squared
summary(Step3_IntentAttachMind)$adj.r.squared - summary(Step2_IntentAttachment)$adj.r.squared

anova(Step1_Intent_ECR, Step2_IntentAttachment, Step3_IntentAttachMind)


```
